Solar jet observed at the limb in SDO/SST

### 2016-08-15 paper/ms_temp_paper.tex
minor changes

The feature is also visible in higher coronal lines, however it does appear just below the solar limb as

>>>>

Lastly we find that the jet has a rotational component to its motion.
We find that the jet has rotational velocities that maximise at the tip of the jet as the rotation initialises during the second acceleration of plasma.
After this onset 'untwisting' at the tip of the macrospicule, the unwinding spreads down the feature until we observe a division 50/50 red/blue, with the RHS initially moving away from us.
